Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE)

### 2014-02-14 WSSSPE1_report/WSSSPE1_summary_report.tex
small changes

\begin{itemize}
    \item github
    \item mvapich
    \item Cactus
    \item visTrails
    \item MINRES-QLP
    \item SimGrid
    \item Swift
    \item Galaxy
    \item FastMath and package managers
    \item R/qtl
    \item OWL/RDF
    \item AMR/multiphysics
    \item DUNE
    \item PAAS
    \item Gateways
    \item Globus-Genomics
\end{itemize}

In this section, we discuss the following:
\begin{itemize}
    \item Categorize the real-world software projects into workshop themes. This is based on the aspect of a software project that dominates and best fits one of the workshop themes.
    \item Discuss how the theme has impacted software projects over its lifetime.
    \item Discuss similarities and differences between these projects.
    \item What is a takeaway for a new project? What are the lessons learned? How can the course of current and future development projects be altered to implement lessons learned.
\end{itemize}

The software projects discussed in the workshop can be classified as follows:

- General Purpose
    Software that enables other software to run by providing suitable environment. eg. Collaborative development, Workflow and scripting frameworks

- Special Purpose
Software that was developed specifically for a target use-case scenario or keeping some fixed requirements in mind.

--Science Oriented
      Software developed to solve domain science problems eg. MINRES-QLP

--Infrastructure Oriented
      Software developed to better utilize new infrastructure, eg. MVAPICH

>>>>

\begin{itemize}
    \item mvapich, Cactus, DUNE
    \item gateways, github, VisIT, visTrails, PAAS
    \item SimGrid, Swift, Galaxy
    \item FastMath, R/qtl, MINRES-QLP
    \item OWL/RDF, AMR/multiphysics, Globus-Genomics
\end{itemize}

In this section, we discuss the following:
\begin{itemize}
    \item Categorize the real-world software projects into workshop themes. This is based on the aspect of a software project that dominates and best fits one of the workshop themes.
    \item How the worshop themes are applicable to and has impacted software projects over its lifetime.
    \item Similarities and differences between these projects.
    \item What is a takeaway for a new project? What are the lessons learned? How can the course of current and future development projects be altered to implement lessons learned.
\end{itemize}

The software projects discussed in the workshop can be classified as follows:
\begin{itemize}
\item General Purpose Software applicable to a generic task and/or enabling other software to run by providing suitable environment. eg. Collaborative development, Workflow and scripting frameworks, visualization frameworks.
\item Special Purpose Software that was developed specifically for a target use-case scenario or keeping some fixed/frozen requirements in mind.
\begin{itemize}
  \item Domain science oriented software developed to solve domain science problems, eg. MINRES-QLP.
  \item Infrastructure oriented software developed to better utilize new infrastructure, eg. MVAPICH.
\end{itemize}
\end{itemize}

A recurrent theme of the workshop was following best practices while developing software. Many submissions discuss software development best practices.
